Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-01-19 paper/main.tex
Revise introduction

Here we present a series of experiments measuring the kinematics and lift forces produced by eleven
differently sized wings flapping at multiple speeds and amplitudes with Reynolds numbers between
2500 and 5000. Several quasi-steady models from the literature are shown to exhibit strong agreement
with the experimental data.  Then a set of data-driven equations were automatically generated from
the data using the symbolic regression algorithm developed by Schmidt and Lipson \cite{schmidt2009distilling}.
These data-driven models exhibit several remarkable properties.  First, they are at least as
accurate as quasi-steady equations from the literature yet they are much simpler.  Second, they
naturally separate distinct, understandable physical effects including terms corresponding to
inertial forces and aerodynamic lift.  Finally, it is shown that models generated from data of a
single experiment do not have the property of separating distinct physical effects, and they fail to
accurately predict forces produced by a wing of a different geometry or flapping pattern.  It is
only when models are trained on a large set of experiments including many different wings and
flapping patterns that over-fit candidate equations are discarded and those that reflect the true
underlying physics are maintained.  The models trained on a diverse set of data are shown to
accurately predict the forces produced by wings of similar size and flapping kinematics that were
not included in the training set. The ability of the symbolic regression process to infer distinct
physical contributions to to the total lift force based on data alone suggests it may be a powerful
tool in identifying the underlying structure of a wide variety of complex systems.

>>>>

Here we present a series of experiments measuring the kinematics and lift forces produced by eleven
differently sized wings flapping at multiple speeds and amplitudes with Reynolds numbers between
2500 and 5000. Several quasi-steady models from the literature are shown to exhibit strong agreement
with the experimental data. Then a set of data-driven equations were automatically generated from
the data using the symbolic regression algorithm developed by Schmidt and Lipson
\cite{schmidt2009distilling}. These data-driven models exhibit several desirable properties. First,
they are at least as accurate as quasi-steady equations from the literature yet they are much
simpler.  Second, they naturally separate distinct, understandable physical effects including terms
corresponding to inertial forces and aerodynamic lift. Finally, they generalize well, providing
accurate force predictions for similar experiments outside their training dataset, indicating that
they correctly identify and assemble the most salient and predictive variables. These results
indicate that data-driven symbolic regression may be a powerful scientific tool in discovering the
underlying structure of many complex systems, as well as providing a practical tool in challenging
engineering tasks like flapping wing design optimization.
